---
output: rmarkdown::github_document
---

```{r, include=FALSE}
library(feather)
```

## Introduction

This package contains a selection of colour palettes inspired by the plumage of Australian birds.


## Installation

This package is hosted on GitHub and can be installed using the devtools package:

```{r, message=FALSE}
devtools::install_github("shandiya/feather")
```


## How to use `feather`

Colour palettes are stored as a list called `feather_palettes`, and can be accessed thus:

```{r}
library(feather)
names(feather_palettes)
```

`get_pal` is a function that returns the chosen palette as a vector of hex colour codes.

```{r}
get_pal("eastern_rosella")
```

`print_pal` is a function that displays the colour palette in the plots pane.

```{r}
eastern_rosella <- get_pal("eastern_rosella")
print_pal(eastern_rosella)
```

## Examples

`ggplot`:

```{r, message=FALSE, warning=FALSE}
library(palmerpenguins)
library(tidyverse)

ggplot(penguins) +
  geom_point(aes(flipper_length_mm, body_mass_g, colour = species)) +
  scale_colour_manual(values = get_pal("eastern_rosella"))
```

base `R`:

```{r}
library(palmerpenguins)
plot(penguins$flipper_length_mm, penguins$body_mass_g, col = get_pal("eastern_rosella")[factor(penguins$species)], pch = 19)
```


## Contribute

If you would like to contribute to this package or have suggestions for improvement, please contact [@ShandiyaB](https://twitter.com/ShandiyaB) on Twitter or submit a pull request. 



